oREV item selection

### 2022-11-10 analysis/irt_analysis.Rmd
comp grapohs

```{r setup, include=FALSE}
library(tidyverse)
library(ggpubr)
library(tidyboot)
library(brms)
library(readxl)
library(ggthemes)
library(geomtextpath)
library(coda)
library(ggridges)
library(testing)

@@

@@

kr20(rel_dat, hit = 1)
```

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(ggpubr)
library(tidyboot)
library(brms)
library(readxl)
library(ggthemes)
library(geomtextpath)
library(coda)
library(ggridges)
library(testing)
library(eRm)

@@

### KR20

@@

kr20_rel <- kr20(rel_dat, hit = 1)

kr20_rel
```

### Andrich Reliability

pers_params <- ranef(irt1_guess_sel)$subjID%>%as_tibble(rownames = "subjID")

sep_rel <- 1 - 
  (1/length(pers_params$Estimate.eta_Intercept) * sum(pers_params$Est.Error.eta_Intercept^2))/
  (1/(length(pers_params$Estimate.eta_Intercept)-1)*sum((pers_params$Estimate.eta_Intercept - mean(pers_params$Estimate.eta_Intercept))^2))

sep_rel
```

### 2022-11-10 analysis/item_selection.Rmd
comp grapohs

```{r}
rasch_fit <- irt_dat%>%
  left_join(aoa)%>%
  select(-order, -sex)%>%
  filter(targetWord %in% rasch_selected_items,
         #subjID %in% c("15X7mwV1", "39tVizn3", "479FefBH")
         )%>%
  add_epred_draws(irt1_guess_sel, re_formula = ~(1 | targetWord) + (1 | subjID), ndraws = 5000)%>%
  mutate(zvi = (correct - .epred)/(.epred*(1-.epred))^0.5)%>%
  group_by(targetWord,aoa_german_comb, .draw)%>%
  summarise(outfit = sum(zvi^2)/length(unique(subjID)),
            infit = (sum(zvi^2*(.epred*(1-.epred)))/sum(.epred*(1-.epred))))

@@

saveRDS(rasch_sel_items, "../saves/rasch_selected_items.rds")
```

@@

```{r}
bind_rows(rasch_fit_sel_guess%>%mutate(fit = "selected items only"),
          rasch_fit%>%mutate(fit = "all items"))%>%
  filter(targetWord %in% rasch_selected_items)%>%
  pivot_longer(names_to = "fit_index", values_to = "value", cols = c(outfit, infit))%>%
  ggplot(. , aes(y = fct_reorder(targetWord, aoa_german_comb), x = value, fill = fit_index, col = fit_index, lty = fit, pch = fit))+
  geom_vline(xintercept = c(0.5, 1.5), lty = 2, alpha = .5)+
  geom_vline(xintercept = c(0.7, 1.3), lty = 3, alpha = .5)+
  geom_vline(xintercept = 1, lty = 1, alpha = .5, col = "darkgreen")+
  stat_halfeye(alpha = .75, .width = c(0.66, 0.95), position = position_dodge(width = 0.9))+
  scale_fill_colorblind()+
  scale_color_colorblind()+
  labs(x = "Index value", y = "Target word (sorted by rated age of acquisition)")+
  #facet_grid(~fit_index)+
  xlim(0,3)+
  theme_bw()
```
```{r}
ggsave("../graphs/fit_index_comp.png", height = 12, width = 10, scale = 1)
```

@@

```{r}
bind_rows(icc1_guess_sel%>%mutate(model = "1PL + guessing"),
          icc3_sel%>%mutate(model = "2PL + guessing")) %>% 
  ggplot(aes(x = theta, y = p,group = interaction(item,model), col = model)) +
  geom_line() +
  facet_wrap(~item)+
  #guides(col = F)+
  geom_hline(yintercept = 0.25, lty = 3, alpha = .75)+
  scale_color_solarized(name = "Model") +
  labs(title = "Comparing ICCs for 1PL and 2PL",
       x = expression(theta~('ability on the logit scale')),
       y = expression(italic(p)(y==1))) +
  ylim(0,1)+
  theme_minimal()
```
```{r}
ggsave("../graphs/fit_index_comp.png", height = 10, width = 14, scale = 1)
```

>>>>

## Fit indices

```{r}
rasch_fit <- irt_dat%>%
  left_join(aoa)%>%
  select(-order, -sex)%>%
  filter(targetWord %in% rasch_selected_items,
         #subjID %in% c("15X7mwV1", "39tVizn3", "479FefBH")
         )%>%
  add_epred_draws(irt1_guess, re_formula = ~(1 | targetWord) + (1 | subjID), ndraws = 5000)%>%
  mutate(zvi = (correct - .epred)/(.epred*(1-.epred))^0.5)%>%
  group_by(targetWord,aoa_german_comb, .draw)%>%
  summarise(outfit = sum(zvi^2)/length(unique(subjID)),
            infit = (sum(zvi^2*(.epred*(1-.epred)))/sum(.epred*(1-.epred))))

@@

@@

```{r}
bind_rows(rasch_fit_sel_guess%>%mutate(fit = "selected items only"),
          rasch_fit%>%mutate(fit = "all items"))%>%
  filter(targetWord %in% rasch_selected_items)%>%
  pivot_longer(names_to = "fit_index", values_to = "value", cols = c(outfit, infit))%>%
  ggplot(. , aes(y = fct_reorder(targetWord, aoa_german_comb), x = value, fill = fit_index, col = fit_index, lty = fit, pch = fit))+
  geom_vline(xintercept = c(0.5, 1.5), lty = 2, alpha = .5)+
  geom_vline(xintercept = c(0.7, 1.3), lty = 3, alpha = .5)+
  geom_vline(xintercept = 1, lty = 1, alpha = .5, col = "darkgreen")+
  stat_halfeye(alpha = .75, .width = c(0.66, 0.95), position = position_dodge(width = 0.9))+
  scale_fill_colorblind()+
  scale_color_colorblind()+
  labs(title = "Comparing In- and Outfit for 1PL + guessing model with all items vs. selected items",
       x = "Index value", y = "Target word (sorted by rated age of acquisition)")+
  #facet_grid(~fit_index)+
  xlim(0,3)+
  theme_bw()
```
```{r}
ggsave("../graphs/fit_index_comp.png", height = 12, width = 10, scale = 1)
```

@@

```{r}
bind_rows(icc1_guess_sel%>%mutate(model = "1PL + guessing"),
          icc3_sel%>%mutate(model = "2PL + guessing")) %>% 
  ggplot(aes(x = theta, y = p,group = interaction(item,model), col = model)) +
  geom_line() +
  facet_wrap(~item, nrow = 2)+
  #guides(col = F)+
  geom_hline(yintercept = 0.25, lty = 3, alpha = .75)+
  scale_color_solarized(name = "Model") +
  labs(title = "Comparing ICCs for 1PL and 2PL",
       x = expression(theta~('ability on the logit scale')),
       y = expression(italic(p)(y==1))) +
  ylim(0,1)+
  theme_bw()
```
```{r}
ggsave("../graphs/ICC_comp.png", height = 4, width = 12, scale = 1.2)
```
